### 2020-07-08 article.tex
Missing caption + scripts

  \subsection{Interfacing HPDDM Krylov methods in PETSc\label{sec:interface-ksp}}\
In this section we provide details of the
interface between HPDDM Krylov methods and the various PETSc
classes. It is assumed that the right-hand sides, and
consequently the solutions, are always dense vectors or matrices.

@@

    \caption{\label{fig:scaling-Ax}}

@@

% Of course, users do not have to implement the three previous steps themselves.
In order to use GenEO from PETSc, the auxiliary operators $\{\mathring{A}_i\}_{i=1}^N$
and the correspondending local to global map of degrees of freedom (see~\cref{fig:poisson})
can be provided using the routine \pk{PCHPDDMSetAuxiliaryMat}.
In special cases where the matrix has been constructed using the PETSc discretization
instrastucture, the relevant information is automatically computed
by PETSc. In \cref{fig:p4est} we provide an example of non-overlapping (left) and overlapping (right)
decomposition using a non-conforming grid with \pk{DMPLEX}~\cite{knepley2009mesh}. The
mesh has been constructed internally by \pk{DMPLEX} using a random pattern of non-conforming 2:1 refinements
and a space-filling curve distribution by p4est~\cite{BursteddeWilcoxGhattas11}.
The required elements needed to properly assemble the Neumann operators in a conforming way are pictured with a lighter color.
Other \pk{DMType}s, including user-defined, may be supported by
implementing the proper \pk{DMCreateNeumannOverlap} callback. Support for \pk{DMDA}
could be easily added upon request.
\begin{figure}[htbp]
  \centering
    \subfloat[Initial nonoverlapping decomposition.]{
        \includegraphics[width=0.45\textwidth]{Data/p4est_nonoverlapping.pdf}
    }
    \subfloat[Overlapping decomposition on which auxiliary operators $\{\mathring{A}_i\}_{i=1}^N$ are assembled.]{
        \includegraphics[width=0.45\textwidth]{Data/p4est_overlapping.pdf}
    }
    \caption{Automatic generation of overlapping subdomains when using a~\pk{DMP4EST}. For clarity, only four subdomains, one of which is disconnected, are colored.\label{fig:p4est}}
\end{figure}

@@

\bibliographystyle{siamplain}
\begin{thebibliography}{10}

\bibitem{adams2004ultra}
{\sc M.~Adams, H.~H. Bayraktar, T.~M. Keaveny, and P.~Papadopoulos}, {\em
  {Ultrascalable Implicit Finite Element Analyses in Solid Mechanics with over
  a Half a Billion Degrees of Freedom}}, in Proceedings of the 2004 ACM/IEEE
  Conference on Supercomputing, SC04, IEEE Computer Society, 2004,
  pp.~\mbox{34:1--34:15}.

\bibitem{aldaas2019multi}
{\sc H.~Al~Daas, L.~Grigori, P.~Jolivet, and P.-H. Tournier}, {\em {A
  Multilevel Schwarz Preconditioner Based on a Hierarchy of Robust Coarse
  Spaces}}, Journal of Scientific Computing,  (2019), p.~submitted for
  publication, \url{https://github.com/prj-/aldaas2019multi}.

\bibitem{amestoy2001fully}
{\sc P.~Amestoy, I.~Duff, J.-Y. L'Excellent, and J.~Koster}, {\em A fully
  asynchronous multifrontal solver using distributed dynamic scheduling}, SIAM
  Journal on Matrix Analysis and Applications, 23 (2001), pp.~15--41,
  \url{http://mumps.enseeiht.fr}.

\bibitem{anderson2019mfem}
{\sc R.~Anderson, J.~Andrej, A.~Barker, J.~Bramwell, J.-S. Camier, J.~Cerveny,
  V.~Dobrev, Y.~Dudouit, A.~Fisher, T.~Kolev, et~al.}, {\em {MFEM: a modular
  finite element methods library}}, arXiv:1911.09220,  (2019),
  \url{http://mfem.org}.

\bibitem{badia2014highly}
{\sc S.~Badia, A.~F. Mart{\'\i}n, and J.~Principe}, {\em A highly scalable
  parallel implementation of balancing domain decomposition by constraints},
  SIAM Journal on Scientific Computing, 36 (2014), pp.~C190--C218.

\bibitem{baker2005technique}
{\sc A.~H. Baker, E.~R. Jessup, and T.~Manteuffel}, {\em {A Technique for
  Accelerating the Convergence of Restarted GMRES}}, SIAM Journal on Matrix
  Analysis and Applications, 26 (2005), pp.~962--984.

\bibitem{balay1997cient}
{\sc S.~Balay, W.~Gropp, L.~Curfman~McInnes, and B.~F. Smith}, {\em Efficient
  management of parallelism in object-oriented numerical software libraries},
  Modern Software Tools in Scientific Computing,  (1997), pp.~163--202.

\bibitem{barrett1994templates}
{\sc R.~Barrett, M.~Berry, T.~F. Chan, J.~Demmel, J.~Donato, J.~Dongarra,
  V.~Eijkhout, R.~Pozo, C.~Romine, and H.~Van~der Vorst}, {\em Templates for
  the solution of linear systems: building blocks for iterative methods}, SIAM,
  1994.

\bibitem{bastian1998additive}
{\sc P.~Bastian, G.~Wittum, and W.~Hackbusch}, {\em Additive and multiplicative
  multi-grid—a comparison}, Computing, 60 (1998), pp.~345--364.

\bibitem{bavier2012amesos2}
{\sc E.~Bavier, M.~Hoemmen, S.~Rajamanickam, and H.~Thornquist}, {\em {Amesos2
  and Belos: Direct and Iterative Solvers for Large Sparse Linear Systems}},
  Scientific Programming, 20 (2012), pp.~241--255.

\bibitem{Benzi2011a}
{\sc M.~Benzi, M.~A. Olshanskii, and Z.~Wang}, {\em {Modified augmented
  Lagrangian preconditioners for the incompressible Navier--Stokes equations}},
  International Journal for Numerical Methods in Fluids, 66 (2011),
  pp.~486--508.

\bibitem{10.1145/3232850}
{\sc W.~Boukaram, G.~Turkiyyah, and D.~Keyes}, {\em {Hierarchical Matrix
  Operations on GPUs: Matrix-Vector Multiplication and Compression}}, ACM
  Transactions on Mathematical Software, 45 (2019).

\bibitem{brown2012composable}
{\sc J.~Brown, M.~G. Knepley, D.~A. May, L.~Curfman~McInnes, and B.~F. Smith},
  {\em Composable linear solvers for multiphysics}, in 2012 11th International
  Symposium on Parallel and Distributed Computing, IEEE, 2012, pp.~55--62.

\bibitem{BursteddeWilcoxGhattas11}
{\sc C.~Burstedde, L.~C. Wilcox, and O.~Ghattas}, {\em {\texttt{p4est}}:
  Scalable algorithms for parallel adaptive mesh refinement on forests of
  octrees}, SIAM Journal on Scientific Computing, 33 (2011), pp.~1103--1133,
  \url{http://www.p4est.org}.

\bibitem{butler2020high}
{\sc R.~Butler, T.~Dodwell, A.~Reinarz, A.~Sandhu, R.~Scheichl, and
  L.~Seelinger}, {\em High-performance dune modules for solving large-scale,
  strongly anisotropic elliptic problems with applications to aerospace
  composites}, Computer Physics Communications, 249 (2020).

\bibitem{cai1999restricted}
{\sc X.-C. Cai and M.~Sarkis}, {\em {A restricted additive Schwarz
  preconditioner for general sparse linear systems}}, SIAM Journal on
  Scientific Computing, 21 (1999), pp.~792--797.

\bibitem{calandra2012flexible}
{\sc H.~Calandra, S.~Gratton, J.~Langou, X.~Pinel, and X.~Vasseur}, {\em
  {Flexible Variants of Block Restarted GMRES Methods with Application to
  Geophysics}}, SIAM Journal on Scientific Computing, 34 (2012),
  pp.~A714--A736.

\bibitem{carvalho2011flexible}
{\sc L.~M. Carvalho, S.~Gratton, R.~Lago, and X.~Vasseur}, {\em {A Flexible
  Generalized Conjugate Residual Method With Inner Orthogonalization and
  Deflated Restarting}}, SIAM Journal on Matrix Analysis and Applications, 32
  (2011), pp.~1212--1235.

\bibitem{da2014isogeometric}
{\sc L.~B. Da~Veiga, L.~F. Pavarino, S.~Scacchi, O.~B. Widlund, and
  S.~Zampini}, {\em {Isogeometric BDDC preconditioners with deluxe scaling}},
  SIAM Journal on Scientific Computing, 36 (2014), pp.~A1118--A1139.

\bibitem{davis2004algorithm}
{\sc T.~A. Davis}, {\em Algorithm 832: {UMFPACK}—an unsymmetric-pattern
  multifrontal method}, ACM Transactions on Mathematical Software, 30 (2004),
  pp.~196--199.

\bibitem{dolean2014ddm}
{\sc V.~Dolean, P.~Jolivet, and F.~Nataf}, {\em An Introduction to Domain
  Decomposition Methods\col\ Algorithms, Theory and Parallel Implementation},
  SIAM, 2015.

\bibitem{erhel1996restarted}
{\sc J.~Erhel, K.~Burrage, and B.~Pohl}, {\em {Restarted GMRES preconditioned
  by deflation}}, Journal of Computational and Applied Mathematics, 69 (1996),
  pp.~303--318.

\bibitem{falgout2002hypre}
{\sc R.~Falgout and U.~Yang}, {\em \emph{hypre}: a library of high performance
  preconditioners}, Computational Science---ICCS 2002,  (2002), pp.~632--641,
  \url{https://www.llnl.gov/casc/hypre}.

\bibitem{frommer2017block}
{\sc A.~Frommer, K.~Lund, and D.~B. Szyld}, {\em {Block Krylov Subspace Methods
  for Functions of Matrices}}, Electronic Transactions on Numerical Analysis,
  47 (2017), pp.~100--126.

\bibitem{gander2006optimized}
{\sc M.~J. Gander}, {\em Optimized {S}chwarz {M}ethods}, SIAM Journal on
  Numerical Analysis, 44 (2006), pp.~699--731.

\bibitem{gee2006ml}
{\sc M.~W. Gee, C.~M. Siefert, J.~J. Hu, R.~S. Tuminaro, and M.~G. Sala}, {\em
  {ML} 5.0 smoothed aggregation user's guide}, Tech. Report SAND2006-2649,
  Sandia National Laboratories, 2006, \url{https://trilinos.github.io/ml.html}.

\bibitem{gutknecht2006block}
{\sc M.~H. Gutknecht}, {\em Block {K}rylov space methods for linear systems
  with multiple right-hand sides: an introduction}, in Modern Mathematical
  Models, Methods and Algorithms for Real World Systems, A.~Siddiqui, I.~Duff,
  and O.~Christensen, eds., 2006, pp.~420--447.

\bibitem{gutknecht2008updating}
{\sc M.~H. Gutknecht and T.~Schmelzer}, {\em {Updating the $QR$ decomposition
  of block tridiagonal and block Hessenberg matrices}}, {Applied Numerical
  Mathematics}, 58 (2008), pp.~871--883.

\bibitem{haferssas2017soras}
{\sc R.~Haferssas, P.~Jolivet, and F.~Nataf}, {\em {An additive Schwarz method
  type theory for Lions's algorithm and a Symmetrized Optimized Restricted
  Additive Schwarz Method}}, Journal on Scientific Computing, 39 (2017),
  pp.~A1345--A1365.

\bibitem{hecht2012new}
{\sc F.~Hecht}, {\em New development in {FreeFem++}}, Journal of Numerical
  Mathematics, 20 (2012), pp.~251--266, \url{http://freefem.org}.

\bibitem{heinecke2016libxsmm}
{\sc A.~Heinecke, G.~Henry, M.~Hutchinson, and H.~Pabst}, {\em {LIBXSMM:
  accelerating small matrix multiplications by runtime code generation}}, in
  Proceedings of the 2016 International Conference for High Performance
  Computing, Networking, Storage and Analysis, SC16, IEEE, 2016,
  \url{https://github.com/hfp/libxsmm}.

\bibitem{Heinlein:2016:PIT}
{\sc A.~Heinlein, A.~Klawonn, and O.~Rheinbach}, {\em A parallel implementation
  of a two-level overlapping {S}chwarz method with energy-minimizing coarse
  space based on {T}rilinos}, SIAM Journal on Scientific Computing, 38 (2016),
  pp.~C713--C747.

\bibitem{hernandez2005ssf}
{\sc V.~Hernandez, J.~E. Roman, and V.~Vidal}, {\em {SLEP}c: A scalable and
  flexible toolkit for the solution of eigenvalue problems}, ACM Transactions
  on Mathematical Software, 31 (2005), pp.~351--362,
  \url{https://slepc.upv.es}.

\bibitem{heroux2005overview}
{\sc M.~A. Heroux, R.~A. Bartlett, V.~E. Howle, R.~J. Hoekstra, J.~J. Hu, T.~G.
  Kolda, R.~B. Lehoucq, K.~R. Long, R.~P. Pawlowski, E.~T. Phipps, et~al.},
  {\em {An overview of the Trilinos project}}, ACM Transactions on Mathematical
  Software (TOMS), 31 (2005), pp.~397--423, \url{https://trilinos.github.io}.

\bibitem{hestenes1952methods}
{\sc M.~R. Hestenes and E.~Stiefel}, {\em {Methods of Conjugate Gradients for
  Solving Linear Systems}}, Journal of Research of the National Bureau of
  Standards, 49 (1952), pp.~409--436.

\bibitem{hoefler2015scientific}
{\sc T.~Hoefler and R.~Belli}, {\em Scientific benchmarking of parallel
  computing systems: twelve ways to tell the masses when reporting performance
  results}, in Proceedings of the 2015 International Conference for High
  Performance Computing, Networking, Storage and Analysis, SC15, 2015.

\bibitem{mkl-web-page}
{\sc Intel}, {\em {MKL} web page}.
\newblock
  \url{https://software.intel.com/content/www/us/en/develop/tools/math-kernel-library.html},
  2020.

\bibitem{ji2017breakdown}
{\sc H.~Ji and Y.~Li}, {\em A breakdown-free block conjugate gradient method},
  BIT Numerical Mathematics, 57 (2017), pp.~379--403.

\bibitem{jolivet2013scalable}
{\sc P.~Jolivet, F.~Hecht, F.~Nataf, and C.~Prud'homme}, {\em {Scalable Domain
  Decomposition Preconditioners for Heterogeneous Elliptic Problems}}, in
  Proceedings of the International Conference on High Performance Computing,
  Networking, Storage and Analysis, SC13, ACM, 2013.

\bibitem{jolivet2016block}
{\sc P.~Jolivet and P.-H. Tournier}, {\em {Block Iterative Methods and
  Recycling for Improved Scalability of Linear Solvers}}, in Proceedings of the
  2016 International Conference for High Performance Computing, Networking,
  Storage and Analysis, SC16, IEEE, 2016.

\bibitem{KALANTZIS2018136}
{\sc V.~Kalantzis, A.~C.~I. Malossi, C.~Bekas, A.~Curioni, E.~Gallopoulos, and
  Y.~Saad}, {\em A scalable iterative dense linear system solver for multiple
  right-hand sides in data analytics}, Parallel Computing, 74 (2018),
  pp.~136--153.

\bibitem{karypis1998fast}
{\sc G.~Karypis and V.~Kumar}, {\em A fast and high quality multilevel scheme
  for partitioning irregular graphs}, SIAM Journal on Scientific Computing, 20
  (1998), pp.~359--392,
  \url{http://glaros.dtc.umn.edu/gkhome/metis/parmetis/overview}.

\bibitem{knepley2009mesh}
{\sc M.~G. Knepley and D.~A. Karpeev}, {\em {Mesh algorithms for PDE with Sieve
  I: Mesh distribution}}, Scientific Programming, 17 (2009), pp.~215--230.

\bibitem{knyazev2001toward}
{\sc A.~V. Knyazev}, {\em {Toward the optimal preconditioned eigensolver:
  Locally optimal block preconditioned conjugate gradient method}}, SIAM
  journal on scientific computing, 23 (2001), pp.~517--541.

\bibitem{lehoucq1998arpack}
{\sc R.~Lehoucq, D.~Sorensen, and C.~Yang}, {\em {ARPACK} users’ guide\col\
  solution of large-scale eigenvalue problems with implicitly restarted Arnoldi
  methods}, vol.~6, Society for Industrial and Applied Mathematics, 1998,
  \url{http://www.caam.rice.edu/software/ARPACK}.

\bibitem{li2005overview}
{\sc X.~S. Li}, {\em {An overview of SuperLU: Algorithms, implementation, and
  user interface}}, ACM Transactions on Mathematical Software, 31 (2005),
  pp.~302--325.

\bibitem{li2003superlu_dist}
{\sc X.~S. Li and J.~Demmel}, {\em {SuperLU\_DIST: A scalable
  distributed-memory sparse direct solver for unsymmetric linear systems}}, ACM
  Transactions on Mathematical Software, 29 (2003), pp.~110--140.

\bibitem{mandel1993balancing}
{\sc J.~Mandel}, {\em Balancing domain decomposition}, Communications in
  Numerical Methods in Engineering, 9 (1993), pp.~233--241.

\bibitem{marchand2019two}
{\sc P.~Marchand, X.~Claeys, P.~Jolivet, F.~Nataf, and P.-H. Tournier}, {\em
  {Two-level preconditioning for $h$-version boundary element approximation of
  hypersingular operator with GenEO}}, Numerische Mathematik,  (2019),
  p.~submitted for publication.

\bibitem{mathew2008domain}
{\sc T.~Mathew}, {\em Domain decomposition methods for the numerical solution
  of partial differential equations}, vol.~61, Springer Science \& Business
  Media, 2008.

\bibitem{may2016extreme}
{\sc D.~A. May, P.~Sanan, K.~Rupp, M.~G. Knepley, and B.~F. Smith}, {\em
  {Extreme-scale multigrid components within PETSc}}, in Proceedings of the
  Platform for Advanced Scientific Computing Conference, 2016.

\bibitem{moulin2018al}
{\sc J.~Moulin, P.~Jolivet, and O.~Marquet}, {\em {Augmented Lagrangian
  Preconditioner for Large-Scale Hydrodynamic Stability Analysis}}, Computer
  Methods in Applied Mechanics and Engineering, 351 (2019), pp.~718--743,
  \url{https://github.com/prj-/moulin2019al}.

\bibitem{notay2000flexible}
{\sc Y.~Notay}, {\em Flexible conjugate gradients}, SIAM Journal on Scientific
  Computing, 22 (2000), pp.~1444--1460.

\bibitem{cusparse-web-page}
{\sc NVIDA}, {\em {cuSPARSE} web page}.
\newblock \url{https://docs.nvidia.com/cuda/cusparse/}, 2020.

\bibitem{oh2018bddc}
{\sc D.-S. Oh, O.~B. Widlund, S.~Zampini, and C.~Dohrmann}, {\em {BDDC
  algorithms with deluxe scaling and adaptive selection of primal constraints
  for Raviart--Thomas vector fields}}, Mathematics of Computation, 87 (2018),
  pp.~659--692.

\bibitem{o1980block}
{\sc D.~P. O'Leary}, {\em {The Block Conjugate Gradient Algorithm and Related
  Methods}}, Linear Algebra and its Applications, 29 (1980), pp.~293--322.

\bibitem{parks2006recycling}
{\sc M.~L. Parks, E.~de~Sturler, G.~Mackey, D.~D. Johnson, and S.~Maiti}, {\em
  {Recycling Krylov Subspaces for Sequences of Linear Systems}}, SIAM Journal
  on Scientific Computing, 28 (2006), pp.~1651--1674.

\bibitem{pechstein2012finite}
{\sc C.~Pechstein}, {\em {Finite and Boundary Element Tearing and
  Interconnecting Solvers for Multiscale Problems}}, vol.~90 of Lecture Notes
  in Computational Science and Engineering, Springer, 2012.

\bibitem{pechstein2017unified}
{\sc C.~Pechstein and C.~R. Dohrmann}, {\em {A unified framework for adaptive
  BDDC}}, Electronic Transactions on Numerical Analysis, 46 (2017),
  pp.~273--336.

\bibitem{poulson2013elemental}
{\sc J.~Poulson, B.~Marker, R.~A. Van~de Geijn, J.~R. Hammond, and N.~A.
  Romero}, {\em {Elemental: A new framework for distributed memory dense matrix
  computations}}, ACM Transactions on Mathematical Software, 39 (2013).

\bibitem{quarteroni1999domain}
{\sc A.~Quarteroni and A.~Valli}, {\em Domain decomposition methods for partial
  differential equations}, vol.~10, Clarendon Press, 1999.

\bibitem{saad1993flexible}
{\sc Y.~Saad}, {\em {A Flexible Inner--Outer Preconditioned GMRES Algorithm}},
  SIAM Journal on Scientific Computing, 14 (1993), pp.~461--469.

\bibitem{saad2003iterative}
{\sc Y.~Saad}, {\em {Iterative Methods for Sparse Linear Systems}}, SIAM, 2003.

\bibitem{saad1986gmres}
{\sc Y.~Saad and M.~H. Schultz}, {\em {GMRES: a generalized minimal residual
  algorithm for solving nonsymmetric linear systems}}, SIAM Journal on
  Scientific and Statistical Computing, 7 (1986), pp.~856--869.

\bibitem{saad2000deflated}
{\sc Y.~Saad, M.~Yeung, J.~Erhel, and F.~Guyomarc'h}, {\em A deflated version
  of the conjugate gradient algorithm}, SIAM Journal on Scientific Computing,
  21 (2000), pp.~1909--1926.

\bibitem{sakurai2003projection}
{\sc T.~Sakurai and H.~Sugiura}, {\em A projection method for generalized
  eigenvalue problems using numerical integration}, Journal of Computational
  and Applied Mathematics, 159 (2003), pp.~119--128.

\bibitem{sakurai2010application}
{\sc T.~Sakurai, H.~Tadano, and Y.~Kuramashi}, {\em {Application of block
  Krylov subspace algorithms to the Wilson--Dirac equation with multiple
  right-hand sides in lattice QCD}}, Computer Physics Communications, 181
  (2010), pp.~113--117.

\bibitem{si2013tet}
{\sc H.~Si}, {\em {TetGen: A Quality Tetrahedral Mesh Generator and 3D Delaunay
  Triangulator}}, Tech. Report~13, 2013,
  \url{http://wias-berlin.de/software/tetgen}.

\bibitem{vsistek2013parallel}
{\sc J.~{\v{S}}{\'\i}stek, J.~Mandel, B.~Soused{\'\i}k, and P.~Burda}, {\em
  Parallel implementation of multilevel {BDDC}}, in Numerical Mathematics and
  Advanced Applications 2011, Springer, 2013, pp.~681--689,
  \url{http://users.math.cas.cz/~sistek/software/bddcml.html}.

\bibitem{smith2004domain}
{\sc B.~F. Smith, P.~Bj{\o}rstad, and W.~Gropp}, {\em Domain decomposition:
  parallel multilevel methods for elliptic partial differential equations},
  Cambridge University Press, 2004.

\bibitem{soodhalter2014krylov}
{\sc K.~M. Soodhalter, D.~B. Szyld, and F.~Xue}, {\em Krylov subspace recycling
  for sequences of shifted linear systems}, Applied Numerical Mathematics, 81
  (2014), pp.~105--118.

\bibitem{spillane2011robust}
{\sc N.~Spillane, V.~Dolean, P.~Hauret, F.~Nataf, C.~Pechstein, and
  R.~Scheichl}, {\em A robust two-level domain decomposition preconditioner for
  systems of {PDE}s}, Comptes Rendus Mathématique, 349 (2011), pp.~1255--1259.

\bibitem{spillane2013abstract}
{\sc N.~Spillane, V.~Dolean, P.~Hauret, F.~Nataf, C.~Pechstein, and
  R.~Scheichl}, {\em Abstract robust coarse spaces for systems of {PDEs} via
  generalized eigenproblems in the overlaps}, Numerische Mathematik, 126
  (2013), pp.~741--700.

\bibitem{spillane2013automatic}
{\sc N.~Spillane and D.~J. Rixen}, {\em Automatic spectral coarse spaces for
  robust finite element tearing and interconnecting and balanced domain
  decomposition algorithms}, International Journal for Numerical Methods in
  Engineering, 95 (2013), pp.~953--990.

\bibitem{stathopoulos2002block}
{\sc A.~Stathopoulos and K.~Wu}, {\em {A Block Orthogonalization Procedure with
  Constant Synchronization Requirements}}, SIAM Journal on Scientific
  Computing, 23 (2002), pp.~2165--2182.

\bibitem{Stewart2002}
{\sc G.~W. Stewart}, {\em {A Krylov--Schur Algorithm for Large Eigenproblems}},
  SIAM Journal on Matrix Analysis and Applications, 23 (2002), pp.~601--614.

\bibitem{tang2009comparison}
{\sc J.~Tang, R.~Nabben, C.~Vuik, and Y.~Erlangga}, {\em Comparison of
  two-level preconditioners derived from deflation, domain decomposition and
  multigrid methods}, Journal of Scientific Computing, 39 (2009), pp.~340--370.

\bibitem{toselli2005domain}
{\sc A.~Toselli and O.~B. Widlund}, {\em Domain decomposition methods:
  algorithms and theory}, vol.~34 of Series in Computational Mathematics,
  Springer, 2005.

\bibitem{tournier2016micro}
{\sc P.-H. Tournier, I.~Aliferis, M.~Bonazzoli, M.~de~Buhan, M.~Darbas,
  V.~Dolean, F.~Hecht, P.~Jolivet, I.~El~Kanfoud, C.~Migliaccio, F.~Nataf,
  C.~Pichot, and S.~Semenov}, {\em {Microwave Tomographic Imaging of
  Cerebrovascular Accidents by Using High-Performance Computing}}, Parallel
  Computing, 85 (2019), pp.~88--97.

\bibitem{van1992bi}
{\sc H.~A. Van~der Vorst}, {\em {Bi-CGSTAB: a fast and smoothly converging
  variant of Bi-CG for the solution of nonsymmetric linear systems}}, SIAM
  Journal on Scientific and Statistical Computing, 13 (1992), pp.~631--644.

\bibitem{wakam2013158}
{\sc D.~N. Wakam and F.~Pacull}, {\em Memory efficient hybrid algebraic solvers
  for linear systems arising from compressible flows}, Computers \& Fluids, 80
  (2013), pp.~158--167.

\bibitem{zampini2016pcbddc}
{\sc S.~Zampini}, {\em {PCBDDC: a class of robust dual--primal methods in
  PETSc}}, SIAM Journal on Scientific Computing, 38 (2016), pp.~S282--S306,
  \url{https://www.mcs.anl.gov/petsc/petsc-master/docs/manualpages/PC/PCBDDC.html}.

\bibitem{zampini2017balancing}
{\sc S.~Zampini, P.~Vassilevski, V.~Dobrev, and T.~Kolev}, {\em {Balancing
  Domain Decomposition by Constraints Algorithms for Curl-Conforming Spaces of
  Arbitrary Order}}, in International Conference on Domain Decomposition
  Methods, Springer, 2017, pp.~103--116.

\end{thebibliography}
\end{document}

>>>>

  \subsection{Interfacing HPDDM Krylov methods in PETSc\label{sec:interface-ksp}}\
In this section, we provide details of the
interface between HPDDM Krylov methods and the various PETSc
classes. It is assumed that the right-hand sides, and
consequently the solutions, are always dense vectors or matrices.

@@

    \caption{Scalability of \pk{MatMult} with \pk{MatAIJMKL} and different number of processes.\label{fig:scaling-Ax}}

@@

% Of course, users do not have to implement the three previous steps themselves.
In order to use GenEO from PETSc, the auxiliary operators $\{\mathring{A}_i\}_{i=1}^N$
and the correspondending local to global map of degrees of freedom (see~\cref{fig:poisson})
can be provided using the routine \pk{PCHPDDMSetAuxiliaryMat}.
In special cases where the matrix has been constructed using the PETSc discretization
instrastucture, the relevant information is automatically computed
by PETSc. \Cref{fig:nonoverlapping} (resp.~\cref{fig:overlapping}) is an
example of a non-overlapping (resp. overlapping) decomposition using a
non-conforming grid with \pk{DMPLEX}~\cite{knepley2009mesh}. The
mesh has been constructed internally by \pk{DMPLEX} using a random pattern of non-conforming 2:1 refinements
and a space-filling curve distribution by p4est~\cite{BursteddeWilcoxGhattas11}.
The required elements needed to properly assemble the Neumann operators in a conforming way are pictured with a lighter color.
Other \pk{DMType}s, including user-defined, may be supported by
implementing the proper \pk{DMCreateNeumannOverlap} callback. Support for \pk{DMDA}
could be easily added upon request.
\begin{figure}[htbp]
  \centering
    \subfloat[Initial non-overlapping decomposition.\label{fig:nonoverlapping}]{
        \includegraphics[width=0.45\textwidth]{Data/p4est_nonoverlapping.pdf}
    }
    \subfloat[Overlapping decomposition on which auxiliary operators $\{\mathring{A}_i\}_{i=1}^N$ are assembled.\label{fig:overlapping}]{
        \includegraphics[width=0.45\textwidth]{Data/p4est_overlapping.pdf}
    }
    \caption{Automatic generation of overlapping subdomains when using a~\pk{DMP4EST}. For clarity, only four subdomains, one of which is disconnected, are colored.\label{fig:p4est}}
\end{figure}

@@

\bibliographystyle{siamplain}
\bibliography{article.bib , ../../2018/SC18/bare_conf.bib , ../../2016/SC16/bare_conf.bib , ../../../Courses/2019/Tokyo/main.bib , ../../../Bibliography/main.bib , ../../../CV/cv.bib}
\end{document}
